---
title: "Choroplethr"
---

`choroplethr` was designed to make it as easy as possible to do exploratory data analysis of demographic data using choropleth (i.e. color-coded) maps. 

As an example, let's use `choroplethr` to explore the built-in dataset `?df_pop_county`, which has 2012 county-level population estimates. We will create the map using `?county_choropleth`.

```{r}
#| message: false
library(choroplethr)
library(choroplethrMaps)

data(df_pop_county)
county_choropleth(df_pop_county)
```
`choroplethr` defaults to using 7 quantiles. This means that there are 7 unique colors, and an equal number of counties are assigned to each color. 

If you use two quantiles, you can see which counties have above or blow the median
population:
```{r}
library(choroplethr)
library(choroplethrMaps)

data(df_pop_county)
county_choropleth(df_pop_county, num_colors=2)
```

Using a continuous scale for the colors makes it easy to detect outliers. You can
do that by setting `num_colors=1`:

```{r}
library(choroplethr)
library(choroplethrMaps)

data(df_pop_county)
county_choropleth(df_pop_county, num_colors=1)
```

To learn more take the free class [Mapmaking in R with Choroplethr](https://ari-lamsteins-courses.thinkific.com/courses/mapmaking-in-r-with-choroplethr)